Simulations of Ballot Polling Risk-Limiting Audits

### 2022-01-09 MultipleRoundSims/sections/04-expts.tex
reviews cont.

%Definitions
In this section, we motivate and describe the experiments. We consider a two candidate plurality contest, and assume that ballots are sampled with replacement, as is common in the literature. Note that \BRAVO and \Minerva can be extended for multiple-candidate, multiple-winner plurality contests by performing pairwise audits between the winners and the losers\cite{RLA, arxiv_athena}. Therefore, a two candidate plurality contest can be thought of as the most general case, and our simulations provide insight for multiple-candidate and multiple-winner contests too.

>>>>

%Definitions
In this section, we motivate and describe the experiments. We consider a two candidate plurality contest, and assume that ballots are sampled with replacement, as is common in the literature. Note that sampling without replacement is more efficient as sampling fractions grow, but \Minerva has not been extended for sampling without replacement. Note that both \BRAVO and \Minerva can be extended for multiple-candidate, multiple-winner plurality contests by performing pairwise audits between the winners and the losers\cite{RLA, arxiv_athena}. Therefore, a two candidate plurality contest can be thought of as the most general case, and our simulations provide insight for multiple-candidate and multiple-winner contests too.
